Patterns of floral and chromosome evolution in Onagraceae: a fossil-calibrated supermatrix analysis

### 2014-05-06 manuscript.tex
title change
added chromosome figure and abstract

\usepackage{lineno}
\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{adjustbox}
\usepackage{natbib}
\usepackage{booktabs}
\modulolinenumbers[5]

@@

\title{Fossil-calibrated supermatrix phylogeny of Onagraceae: patterns of floral and chromosome evolution}

@@

\begin{abstract}
blah blah
\end{abstract}

@@

\linenumbers

@@

\paragraph{Character state reconstruction}
I scored six characters, including
chromosome number, floral merosity, petal color, and self-compatibility/incompatibility. 
Character data was assembled from the comprehensive \citet{wagner2007revised} Onagraceae monograph.
Ancestral character state reconstructions of petal number and petal color were performed using Mesquite v2.75 \citep{mesquite}
over the Bayesian MCC tree.
Characters were treated as unordered categorical data, and optimized using maximum likelihood
with the Markov k-state 1 parameter (Mk1) model \citep{lewis2001likelihood}.

@@

>>>>

\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{adjustbox}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{lineno}

@@

\title{Patterns of floral and chromosome evolution in Onagraceae: a fossil-calibrated supermatrix analysis}

@@

\begin{abstract}
Onagraceae is a cosmopolitan plant family in the order Myrtales comprised of 22 genera and 657 species.
I used a GenBank data-mining approach to construct an 11 gene supermatrix of 521 taxa in Onagraceae and Lythraceae.
Maximum likelihood and Bayesian inference phylogenetic analyses were performed, 
and divergence time estimates were calibrated using 5 fossils.
Chromosome number evolution was estimated using probabilistic models,
and ancestral states of petal color and petal number were reconstructed using maximum likelihood.
Correlated evolution between petal color and petal number was tested using
stochastic character mapping.
The monophyly of all major clades in Onagraceae was supported,
and Onagraceae was estimated to have diverged from Lythraceae 109 Mya. 
The base chromosome number of Onagraceae was inferred to be $x=5$.
Petal color and petal number were found
to follow a pattern of correlated evolution ($p=0.00$), 
suggesting concerted shifts in floral traits may play an important role shaping diversification of Onagraceae. 
\end{abstract}

@@

%\modulolinenumbers[5]
%\linenumbers

@@

\paragraph{Character state reconstruction}
I scored six characters, including
chromosome number, floral merosity, petal color, and self-compatibility/incompatibility. 
Character data was assembled from the comprehensive \citet{wagner2007revised} Onagraceae monograph.
Ancestral character state reconstructions of petal number and petal color were performed using Mesquite v2.75 \citep{mesquite}
over the Bayesian MCC tree.
Characters were treated as unordered categorical data, and optimized using maximum likelihood
with the Markov k-state 1 parameter (Mk1) model \citep{lewis2001likelihood}.
Ancestral chromosome numbers were inferred using maximum likelihood and Bayesian methods 
as implemented in ChromEvol 2.0 \citep{chromevol}.
Eight different models of chromosome evolution were fit to the Bayesian MCC phylogeny using ChromEvol,
and the best fit model was selected using Akaike's information criterion \citep{aic}.

@@

\begin{figure*}[p]
    \vspace*{-2cm}
    \makebox[\linewidth]{
        \includegraphics[width=1.6\linewidth, trim=0 0 0 0, clip=true]{chromtree_labeled}
    }
    \caption{
    Maximum likelihood estimates of ancestral chromosome numbers over the Bayesian MCC phylogeny
    using the 4 parameter ($\lambda$, $\delta$, $\mu$, $\rho$) model of chromosome evolution selected by Akaike's information criterion.
    The base number of Onagraceae is inferred to be $x=5$.
    }
    \label{chromtree}
\end{figure*}
